Computer Science House Constitution

### 2024-02-28 constitution.tex
Updated qualifications of an RTP (#153)

\asubsubsection{Qualifications of an RTP}
\renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters
\begin{enumerate}
	\item Candidates must have been an On-Floor Active Member in good standing within the last twelve months, or been an Off-Floor Active Member and have lived on the floor within the last twelve months.
	\item Candidates may be granted an exemption by current RTPs.
		Such an exemption may be withdrawn at any time by the current RTPs.
	\item Prior RTPs are those members who are no longer current Active Members and have not been granted an extension by the current RTPs.
		Prior RTPs are not guaranteed access to the current root passwords and other authentication tokens.
	\item The current Root Type Persons may from time to time draft rules and regulations specifying the rights and privileges of Prior RTPs.
\end{enumerate}

>>>>

\asubsubsection{Qualifications of an RTP}
\renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters
\begin{enumerate}
	\item Candidates must be Active Members
\end{enumerate}

\asubsubsection{Prior RTPs}
\begin{enumerate}
	\item Prior RTPs are those members who are no longer current Active Members and have not been granted an extension by the current RTPs.
		Prior RTPs are not guaranteed access to the current root passwords and other authentication tokens.
	\item The current Root Type Persons may from time to time draft rules and regulations specifying the rights and privileges of Prior RTPs.
\end{enumerate}
